--- 
title: "A Minimal Book Example"
author: "Yihui Xie"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: scrreprt
classoption: [
  twoside=true, 
  openright, 
  parskip=full, 
  chapterprefix=true, 
  11pt, 
  headings=normal, 
  bibliography=totoc, 
  listof=totoc, 
  titlepage=on, 
  captions=tableabove, 
  draft=false]
papersize: a4
bibliography: [bib/book.bib, bib/packages.bib, bib/PhD.bib]
biblio-style: unsrtnat
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

<!-- biblio-style: unsrtnat -->
```{r, echo = FALSE}
# Set global options to not show code chunks
knitr::opts_chunk$set(echo = FALSE)
```
# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

For now, you have to install the development versions of **bookdown** from Github:

```{r eval=FALSE}
devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need to install XeLaTeX.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
